{Parallel Implementation of Time Series Analysis in Distributed Database Systems}

### 2013-10-05 draft.tex
Update the figure 1

In\ order to utilize the data parallel capability of MPP database, we
propose to segment the whole time series data into a set of
consecutive time series data, numbering from $1$ to $N$, each subset
comprising a sequence of consecutive time series data of size
$K$. Since the model fitting involves multile iterations of
computations, for any subset $i$ execpt for the first one, we use the
results of the $(i-1)$-th subset from the previous iteration as the
initial values. The first subset's initial values are known to Thus in
each iteration, the computation for each subset of data does not need
to wait for the results from the previous subset. In this way, the
model fitting computaion can be parallelized.

>>>>

In\ order to utilize the data parallel capability of MPP database, we
propose to segment the whole time series data into a set of
consecutive time series data, numbering from $1$ to $N$, each subset
comprising a sequence of consecutive time series data of size
$K$. Since the model fitting involves multile iterations of
computations, for any subset $i$ execpt for the first one, we use the
results of the $(i-1)$-th subset from the previous iteration as the
initial values. The first subset's initial values are known. Thus in
each iteration, the computation for each subset of data does not need
to wait for the results from the previous subset. In this way, the
model fitting computaion can be parallelized.
